\documentclass[11pt,a4paper]{article}

\usepackage[cs,math]{tadocs}
\usepackage{hyperref}

\instructor{Manuel Charlemagne}
\title{ECE4750J\\ Introduction to Cryptography}
\subtitle{Rust Warmup and GMP}
\author{Binhao Qin}
\semester{Summer}
\year{2024}
\blockinfo{
	\quad Goals:
	\begin{itemize}
		\item Get familiar with programming in Rust
		\item Get familiar with Rust build system, \texttt{cargo}
		\item Implement extended Euclidean algorithm using GNU Multi-Precision (GMP) arithmetic library
	\end{itemize}
}

\begin{document}
\maketitle
\section{Rust Warmup}
\begin{enumerate}
	\item Read chapters 1-4, 6.1-2, 8.1-2, 9-11, and 13 of the \href{https://doc.rust-lang.org/book/}{Rust book}.
	\item Complete the Rust warmup exercise.
\end{enumerate}
\section{Extended Euclidean Algorithm}
\begin{enumerate}
	\item Get an environment with GMP installed:
	\begin{itemize}
		\item Install the GNU Multi Precision Arithmetic Library (GMP) from \href{https://gmplib.org/}{https://gmplib.org/} or its fork MPIR available at \href{https://mpir.org/}{https://mpir.org/}. Note that MPIR has a better support for Windows, although no binaries are officially provided. GMP is available on any modern Linux distribution.
		\item Or, use the \texttt{Dockerfile} provided. It has all of the software needed for this course.
	\end{itemize}
	\item Create a new Rust package of type library, implement the extended Euclidean algorithm. (Hint: Check out \texttt{rug}, a Rust package for calling GMP functions)
	\item Write a test that generates 2 random integer, and compares the result of the extended Euclidean algorithm you just implemented to the result of the library function.
	\item Run \texttt{cargo test} to demonstrate that your implementation passes the test.
\end{enumerate}

\end{document}
